---
title: "BreCaNet_clustering"
author: "Ursula Widocki"
date: "10/21/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())

# https://www.bioconductor.org/packages/release/bioc/manuals/genefu/man/genefu.pdf
# libraries to run geneFu
library(genefu)
library(xtable) 
library(rmeta) 
library(Biobase) 
library(caret)

#other libraries

```

```{r}

# HowTo
browseVignettes("genefu")
```

```{r}

subtypePred <- molecular.subtyping(sbt.model = "scmod2", data = ddata, annot = dannot,do.mapping = TRUE)
# sbt.model = "pam50"


```

#Get sample counts pertaining to each subtype
table(SubtypePredictions$subtype)
#Select samples pertaining to Basal Subtype Basals<-names(which(SubtypePredictions$subtype == "ER-/HER2-"))
#Select samples pertaining to HER2 Subtype HER2s<-names(which(SubtypePredictions$subtype == "HER2+"))
#Select samples pertaining to Luminal Subtypes LuminalB<-names(which(SubtypePredictions$subtype == "ER+/HER2- High Prolif")) LuminalA<-names(which(SubtypePredictions$subtype == "ER+/HER2- Low Prolif"))


#ASSIGN SUBTYPES TO EVERY SAMPLE, ADD TO THE EXISTING PHENODATA
ddemo$SCMOD2<-SubtypePredictions$subtype
ddemo[LuminalB,]$SCMOD2<-"LumB"
ddemo[LuminalA,]$SCMOD2<-"LumA"
ddemo[Basals,]$SCMOD2<-"Basal"
ddemo[HER2s,]$SCMOD2<-"Her2"


########################################################################

intrinsic.cluster()
  fit a Single Sample Predictor (SSP) as in Perou, Sorlie, Hu, and Parker publications

intrinsic.cluster.predict()
  identify breast cancer molecular subtypes using the Single Sample Predictor (SSP)

molecular.subtyping()
  Function to identify breast cancer molecular subtypes using the Subtype Clustering Model
  
ps.cluster()
  prediction strength of a clustering model


  
scmgene.robust()
  Subtype Clustering Model using only ESR1, ERBB2 and AURKA genes for identification of breast cancer molecular subtypes
  
scmod1.robust()
  Subtype Clustering Model using ESR1, ERBB2 and AURKA modules for identification of breast cancer molecular subtypes (Desmedt et al 2008)
  
scmod2.robust() 
  Subtype Clustering Model using ESR1, ERBB2 and AURKA modules for identification of breast cancer molecular subtypes (Wirapati et al 2008)



ssp2006()
  SSP2006 classifier for identification of breast cancer molecular sub- types (Hu et al 2006)

pam50()
  parameters defining the PAM50 classifier for identification of breast cancer molecular subtypes


### Older/ Obsolete functions

subtype.cluster()
  Function to fit the Subtype Clustering Model

subtype.cluster.predict()
  Function to identify breast cancer molecular subtypes using the Sub- type Clustering Model




